Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-08-22 tex/main/manuscript.tex
过完讨论第一节

\subsection*{Transition Framework}
% 普遍存在的稳态转换可以由渐变或突变造成，而人类压力在世界范围内都是稳态转换最重要的驱动因素之一。
Widespread regime shifts in a human-water system can be triggered by accumulation of gradual changes, where increasing anthropogenic pressure are among the most important drivers \cite{rochaCascadingRegimeShifts2018a,falkenmarkUnderstandingWaterResilience2019}. 
% 而随着人类干预的加深，水循环出现了自然-社会二元结构，主导当前人水系统的互馈过程。
At the same time, human society has become more and more dependent on water utilization as it further develops, modifying natural water cycles by socio-economic processes \cite{gleesonIlluminatingWaterCycle2020,dibaldassarreSociohydrologyScientificChallenges2019}.
% 与社会-自然二元水循环理论
This social water cycle has linked to the natural water cycle through water withdraw, water utilization and drainage, forming a closed chain of interdependence, interconnection and mutual influence, which is consistent with nature-society dualistic water cycle theory 
\cite{qinTheoreticalFrameworkDualistic2014,liuDualisticWaterCycle2010}.
% 我们的研究结果表明，与社会-生态系统的过渡过程类似，水资源利用体系的变化也存在类似稳态转换的阶段性特征，并最终呈现出自然-社会二元结构。
According to our results, regime shifts as transitional phases of water utilization regimes, similar in social-ecological system, is one of the most important characteristics towards natural-social dualistic structure 
\cite{cummingImplicationsAgriculturalTransitions2014,cummingLinkingEconomicGrowth2018}.
% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
As such, we summarized a transition framework of the water utilization regimes here, which conceptualizes a general trajectory towards a natural-social dualistic water cycle (Figure~\ref{fig:framework}).

@@

% 在水循环向二元系统过渡过程中，存在几个明显的特征。
Towards natural-social binary cycle, there are two obvious features between different transition phases  (figure \ref{fig:framework}).
% 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
Throughout the above transition phases towards binary water cycle, 
three dimensions of water utilization regime are various, following three laws of evolution respectively.
Firstly, although stresses on water resources increases by economic expansion boosting water demands, 
socio-economic progress responding to resource scarcity because of better management and increased water use efficiency. 
For Example...
Secondly, the non-provisioning part of water demands further growths and 
tendentiousness of water utilization continually changes, 
as humans are more dependent on benefits from non-provisioning part of water supply.
Thirdly, With closer socio-economic ties between regions and between regions and river basins, 
the geographic scope of resource supply and demand allocation is expanding, 
leading to changing patterns of water utilization.
By combining the three dimensions, water utilization regimes have a tendency of transitional evolution.

% 综上所述，社会对水资源的利用模式作为一个人-水互馈系统，存在阶段性过渡特征。
For the Yellow River Basin, In addition to the Yellow River Basin, which is the focus of this study, human-water relations in major river basins around the world can be explained by the phases of the transitional framework.
For examples, \dots \dots. In summary, our proposed transitional framework for the nature-society binary water cycle is general in nature.

@@

% 展望：未来还可能陷入结构陷阱，（表现形式：用水效率悖论的同时，灵活性进一步降低，
However, Despite achieving integrated management and escaping through increased water efficiency, 
basins still face new structural traps and require further transformation.
Firstly, in line with paradox of irrigation efficiency \ref{graftonParadoxIrrigationEfficiency2018}, 
significant improvement in agricultural irrigation efficiency (or decline in water use intensity) 
has been accompanied by a resurgence in irrigated area, 
resulting in an unabated and weak upward trend in water stress.
% 水资源压力仍在增大，而节水能力已经进入瓶颈，倾向性贡献减少）
As integrated basin allocation dominates water allocation, 
the propensity to allocate water between non-supply industries, such as industrial services, 
and agriculture is becoming fixed.
At the same time, the flexibility of water use is declining since domestic water use and thermal water use growth rapidly. 
Typically, similar to other cases, these may lead to a reduction in watershed resilience 
and leave highly coupled human-water systems facing greater vulnerability to collapse 
-- a typically structural trap.
% 下一步：可以通过统一调控，调整格局来调整结构，突破结构陷阱。
% 总结：整个流域需进一步转型与适应，以实现高质量发展。
Therefore, based on the identification of the current basin transition stage and development dilemma, 
further transitional governance is still needed to achieve high-quality sustainable development of the basin.

>>>>

\subsection*{Transition Framework}
% 普遍存在的稳态转换可以由渐变或突变造成，而人类压力在世界范围内都是稳态转换最重要的驱动因素之一。
Widespread regime shifts in a human-water system can be triggered by accumulation of gradual changes, where increasing anthropogenic pressure are among the most important drivers \cite{rochaCascadingRegimeShifts2018a,falkenmarkUnderstandingWaterResilience2019}. 
% 而随着人类干预的加深，水循环出现了自然-社会二元结构，主导当前人水系统的互馈过程。
At the same time, human society has become more and more dependent on water utilization as it further develops, modifying natural water cycles by socio-economic processes \cite{gleesonIlluminatingWaterCycle2020,dibaldassarreSociohydrologyScientificChallenges2019}.
% 与社会-自然二元水循环理论
This social water cycle has linked to the natural water cycle through water withdraw, water utilization and drainage, forming a closed chain of interdependence, interconnection and mutual influence, which is consistent with nature-society dualistic water cycle theory 
\cite{qinTheoreticalFrameworkDualistic2014,liuDualisticWaterCycle2010}.
% 我们的研究结果表明，与社会-生态系统的过渡过程类似，水资源利用体系的变化也存在类似稳态转换的阶段性特征，并最终呈现出自然-社会二元结构。
According to our results, regime shifts of water utilization as transitional phases induced by developing, similar in social-ecological system, is one of the most important characteristics towards natural-social dualistic structure 
\cite{cummingImplicationsAgriculturalTransitions2014,cummingLinkingEconomicGrowth2018}.
% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
As such, we summarized a transition framework of the water utilization regimes here, which conceptualizes a general trajectory towards a natural-social dualistic water cycle (Figure~\ref{fig:framework}).

@@

% 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
Throughout the above transition phases towards dualistic water cycle, three dimensions of water utilization regime are various in discipline of evolution, corresponding to typical changes within the Yellow River Basins as an example (Figure~\ref{fig:dimensions}). 
% 水资源压力
(1) Firstly, although stresses on water resources increases by economic expansion boosting water demands, socio-economic progress responding to resource scarcity by better management and efficiency. Water resources were becoming more scarce in the Yellow River Basin from P1 to P3, but the expansion of farmland, the construction of reservoirs, and the increase in water use efficiency became responses to different water utilization stresses in aspects (Figure~\ref{fig:Causes}). Since the scarcity of water resources is directly perceptible and sensitive for utilization, its stresses on societies is one of the most striking drivers to regime shifts within human-water systems \cite{qinFlexibilityIntensityGlobal2019}.
% 水资源倾向性
(2) Secondly, the non-provisioning part of water demands growths with secondary and tertiary industries developing, leading tendentiousness of water utilization continually tilted to the socio-economic part. As original region of Ancient Chinese Civilization, the Yellow River Basin used to be dominated by agricultural but in its way to an energy industry zone now \cite{WillEnergyBases}. As a result, saving water consumption in agriculture and making concessions for industry and energy is widely recognized as solutions for the competing \cite{xiangWillEnergyIndustry2016,bebbWaterRightsTransfers2011}. Anyhow, this changes of tendentiousness reflect a truth that growing socio-economic parts are throwing feedbacks to scarcity of water resources and contributing to regime shifts.
% 水资源格局
(3) Thirdly, with closer socio-economic ties and stiffer competition between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing patterns of water utilization. In the Yellow River Basin, the gap in water consumptions between regions and sectors are narrowing, as the result of a carefully designed allocation \cite{wangThirtyYearsYellow2018}. However, the allocation of water utilization is determined on the basis of regional and sectoral economic contexts and development trajectories\cite{wangThirtyYearsYellow2018}. The changes in water utilization patterns along with regime shifts, therefore, are the outcomes of feedback loops within complex human-water systems.

% 综上所述
By combining the above three dimensions, water utilization regimes reflect a tendency of transitional evolution thoroughly. In addition to the Yellow River Basin, which is the focus of this study, human-water relations in major river basins around the world can be explained by the framework. For examples, Indus River, Mississippi River, and Danube River, whose water utilizations have all gone through a relatively natural phases, rapid developments and integrated management regimes. \cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}. In summary, our proposed transitional framework for the nature-society dualistic water cycle is universal, for identify regime shifts of water utilization.

@@

% 展望：未来还可能陷入结构陷阱，（表现形式：用水效率悖论的同时，灵活性进一步降低，
However, Despite achieving integrated management and escaping through increased water efficiency, 
basins still face new structural traps and require further transformation.
Firstly, in line with paradox of irrigation efficiency \cite{graftonParadoxIrrigationEfficiency2018}, 
significant improvement in agricultural irrigation efficiency (or decline in water use intensity) 
has been accompanied by a resurgence in irrigated area, 
resulting in an unabated and weak upward trend in water stress.
% 水资源压力仍在增大，而节水能力已经进入瓶颈，倾向性贡献减少）
As integrated basin allocation dominates water allocation, 
the propensity to allocate water between non-supply industries, such as industrial services, 
and agriculture is becoming fixed.
At the same time, the flexibility of water use is declining since domestic water use and thermal water use growth rapidly. 
Typically, similar to other cases, these may lead to a reduction in watershed resilience 
and leave highly coupled human-water systems facing greater vulnerability to collapse 
-- a typically structural trap.
% 下一步：可以通过统一调控，调整格局来调整结构，突破结构陷阱。
% 总结：整个流域需进一步转型与适应，以实现高质量发展。
Therefore, based on the identification of the current basin transition stage and development dilemma, 
further transitional governance is still needed to achieve high-quality sustainable development of the basin.
